\huge{Comment on `The Limits of Cosmic Shear'}

### 2016-12-04 theory.tex
Added Catherine's figure with the Cl and xi+.

 \begin{figure}
 \label{fig:Cl_xi}
 \caption{Will show $P_\kappa$ and $\xi_\pm$, TBD}
 \end{figure}

>>>>

 \begin{figure}
 \begin{center}
 \includegraphics[width=0.5\textwidth]{figures/Cl_xi_comp.pdf}
 \label{fig:Cl_xi}
 \caption{\emph{Top:} Theoretical models of the $\kappa$ power spectrum (\emph{left}) and shear correlation function $\xi_+$ (\emph{right})for the different approximations discussed in \citet{kitching/etal:2016}. \emph{Bottom:} Deviations with respect to the full treatment (LSH).}
 \end{center}
 \end{figure}
